A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2012-01-27 papers/contact/paper.tex

\subsection{Hard spheres confined in a cubical cavity}

\textcolor{red}{
  I am thinking of also performing simulations for a cubical cavity, and
  examining the result near the center of a face, which (for a large
  cavity) will give us a prediction for the hard-sphere fluid near a
  single hard wall.  We've got some simulations in
  Figure~\ref{fig:box-density}, but these aren't very nice plots.
  We'll want to do a much larger box, and plot the density vs $x$ near
  the wall.  But I'm waiting on simulation data for this...
}

\subsection{Hard spheres around a hard sphere (or rod)}

\textcolor{red}{
  It would also be interesting to study a system with opposite
  curvature.  Put a (larger) hard sphere in the hard-sphere fluid, and
  see what the contact density is around that hard sphere.  This
  touches on an important limiting case...
}

\begin{figure*}
\includegraphics[height=5cm]{figs/box-100c--05,05,05-13}
\includegraphics[height=5cm]{figs/box-100s--05,05,05-13}
\includegraphics[height=5cm]{figs/box-110c--05,05,05-13}
\caption{Density of hard spheres in a $5\times5\times5$ box.}
\label{fig:box-density}
\end{figure*}

>>>>

\subsection{Hard spheres at a hard wall}

\begin{figure}
  \includegraphics[height=5cm]{figs/walls-10}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.1.}
  \label{fig:walls-10}
\end{figure}

\begin{figure}
  \includegraphics[height=5cm]{figs/walls-30}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.3.}
  \label{fig:walls-30}
\end{figure}

\begin{figure}
  \includegraphics[height=5cm]{figs/walls-40}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.4.}
  \label{fig:walls-40}
\end{figure}

We study the case of hard spheres near a single hard wall.  This is
shown in Figures~\ref{fig:walls-10}-\ref{fig:walls-40}.  Actually, we
should begin with this.

\subsection{Hard spheres around a hard sphere}

It is also interesting to study a system with opposite curvature.  Put
a (larger) hard sphere in the hard-sphere fluid, and see what the
contact density is around that hard sphere.  This is particularly
relevant when we consider using classical density-functional theory to
model solvation.

\begin{figure}
  \includegraphics[height=5cm]{figs/inner-4-30}
  \caption{Density and contact densities around a hard sphere with
    radius 1.}
  \label{fig:inner-4-30}
\end{figure}

\begin{figure}
  \includegraphics[height=5cm]{figs/inner-4-40}
  \caption{Density and contact densities around a hard sphere with
    radius 1.}
  \label{fig:inner-4-40}
\end{figure}

\begin{figure}
  \includegraphics[height=5cm]{figs/inner-8-30}
  \caption{Density and contact densities around a hard sphere with
    radius 3.}
  \label{fig:inner-8-30}
\end{figure}
